Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-24 manu-draft.qmd
added ref about heat stress and light
added Hensel et al to refs

>>>>

Heat stress combined with highlight accelerates decline of *E. acoroides*, used 36C [@zhang2023]

Widgeongrass colonization in Chesapeake Bay as an opportunistic, heat-tolerant species that has replaced Eelgrass, although former is sensitive to nutrient pulses. Paper provides an example of implications on climate change and nutrient management on foundation species and system resiliency [@hensel2023].
